---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blsmarks

<!-- badges: start -->
<!-- badges: end -->

The goal of blsmarks is to automate the process of entering grades into NTU BLS marks spreadsheets.

## Installation

This package is probably never going to be on CRAN because it is just something for people in the Psychology department in NTU.
As such, it should be installed from GitHub.
There are multiple ways of doing this, but one common way is as follows:

``` r
remotes::install_github("mark-andrews/blsmarks")
```

## How to use

Here is an example of how it can be used.
Let's assume you have a data frame in R, let's call it `grades_df`, that has one column named `nid` that indicates the student IDs (N numbers) and another column named `grade` with student grades (in their GBA abbreviated forms like "21HIGH", "DMID" etc).
And let's assume we have a BLS marks Excel spreadsheet like "PSYC40545_29120_M01_CWK_100-202425.xlsx" in the current working directory.
Then, we can use the `enter_bls_grades` command from `blsmarks` package as follows to enter these grades into the spreadsheet:

```{r example, eval=FALSE, echo=TRUE}
library(blsmarks)
enter_bls_grades(grades_df, 
                 "PSYC40545_29120_M01_CWK_100-202425.xlsx", 
                 id_col = 'nid', grade_col = 'grade')
```

This writes the grades to the file.
Note how we indicate which columns of the data frame have the student IDs and the grades.

Also note that the command `enter_bls_grades` will not overwrite an existing grade in the spreadsheet.

## Work in progress; Use with caution

It should go without saying that this is a work in progress and so users should be careful.

It is wise to do two things:

  1. Make a backup of the BLS spreadsheet before running the above command. That command will write content to the spreadsheet. It might do something awry, so having a backed up copy of the original spreadsheet means that in the worst case scenario you can just delete the messed up spreadsheet and go back to the original.
  1. Carefully check whether it worked and that it did what you wanted it or expected it to do.

